Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-04-11 paper/AlignedIsotropicGW.tex
Finished edits.

Estimates of the rate of \ac{BBH} coalescences give a reasonable
chance of 10 additional \ac{BBH} detections in the next two years
\citep{O1-BBH,2016ApJ...833L...1A,2016ApJS..227...14A}.  Assuming \ilya{10} \sout{an}
additional \sout{10} detections with similar observational uncertainties
drawn from each of our six zero-parameter models for the spin
distribution in addition to the three existing detections from O1, we
find the odds ratios shown in Figure \ref{fig:O2-predictions}.  We
find that most scenarios with an additional 10 detections allow the
\sout{correct} \ilya{simulated} angular distribution to be \sout{distinguished} \ilya{inferred} with greater than
$5\sigma$ ($2.9 \times 10^{-7}$ odds) credibility; and in the most
pessimistic case the distinction is typically
$\OTwoSigmaIsoAlignedMin\sigma$ ($\OTwoOddsIsoAlignedMin$ odds ratio).
While such future detections should permit a confident distinction
between \emph{angular} distributions, we would remain much less certain
about the \emph{magnitude} distribution \ilya{among the three options considered here} until we have a larger number
of observations.  In Figure \ref{fig:O2-predictions}, the odds ratio
between different magnitude distributions with the same angular
distribution is much closer to unity than the odds ratio between angular
distributions.

@@

Most of our resolving power for the spin angular distribution is a
result of the fact that our ``aligned'' models cannot produce
$\chieff < 0$ (see Figure \ref{fig:chieff-distribution-models}).  If
spins are intrinsically very small, with $a \lesssim 0.3$, then it is
no longer possible to resolve the negative spin with a small number of
observations.  As noted below, however, spins observed in X-ray
binaries are typically large.  Additionally, models which do not
permit \emph{some} spins with $\chieff \gtrsim 0.1$ are ruled out by
the GW151226 observations \citep{2016PhRvL.116x1103A}.

In order to perform our analysis we need to select models for the
distribution of the spin magnitudes of stellar-mass black holes.
Observational data for such model selection is sparse.
\citet{2015PhR...548....1M} give current estimates of the spin
parameters for stellar-mass black holes, obtained using disk
reflection and/or disk continuum methods.  Most of the systems studied
are low-mass X-ray binaries rather than the high-mass X-ray binaries
that are likely to be the progenitors of double black hole binaries.
In addition, there are substantial systematic errors that can
complicate either type of analysis (see \citealt{2015PhR...548....1M}
for a discussion), and selection effects could yield a biased
distribution. Nonetheless, if we take the reported spin magnitudes as
representative then we find that there is a preference for high spins;
for example, 14 of the 19 systems with reported spins have
dimensionless spin parameters in excess of 0.5.  It is usually argued
that the masses and spin parameters of stellar-mass black holes are
unlikely to be altered significantly by accretion (low-mass donors may
not have enough mass and high-mass donors have a very short phase in
which they transfer mass; a variant of this long-standing argument was
presented by \citet{1999MNRAS.305..654K}), but see
\citet{2003MNRAS.341..385P,2015ApJ...800...17F}.  Thus the current
spin parameters probably are close to their values upon core collapse.
However, the specific processes involved in the production of black
hole binaries from isolated binaries could alter the spin magnitude
distribution of those holes relative to the X-ray binary systems; for
example, close tidal interactions could spin up the core, or stripping
of the envelope could reduce the available angular momentum
\citep{2016MNRAS.462..844K,2017arXiv170200885Z,2017arXiv170203952H}.

@@

The spin directions in isolated binaries, whether evolving via the
classical channel through a common-envelope phase
\citep{TutukovYungelson:1973,TutukovYungelson:1993,Lipunov:1997,2016Natur.534..512B,Stevenson:2017}
or through chemically homogeneous evolution
\citep{MandeldeMink:2016,Marchant:2016} are usually expected to be
preferentially aligned.  Despite observed spin-orbit misalignments in
both massive stellar binaries
\citep{Albrecht:2009,2014ApJ...785...83A} and BH XRBs
\citep{Orosz:2001,Martin:2008b,Martin:2008,MorningstarMiller:2014},
mass accretion and tidal interactions will tend to realign the binary.
On the other hand, a supernova natal kick (if any) can change the
orbital plane and misalign the binary
\citep{2000ApJ...541..319K,2013PhRvD..87j4028G}; the supernova can
also tilt the spin angle, as in the double pulsar J0737-3039
\citep{2011ApJ...742...81F}; and a variety of uncertain processes,
such as wind-driven mass loss and post-collapse fallback, can couple
the spin magnitude and direction distributions, contrary to our
simplified assumptions.

\citet{2017CQGra..34cLT01V} also studied the possibility of
distinguishing aligned and isotropic angular distributions of \ac{BBH}
spins, but concluded that several hundred sources would be required to
adequately separate models which included both parallel and
anti-parallel spins for an ``aligned'' population.  In contrast, and
in agreement with the present study, \citet{Stevenson:2017spin} found
that only $\sim 5$ observations of rapidly spinning black holes would
be necessary to distinguish isotropic and aligned spin distributions,
though tens of detections would be required for more nuanced admixture
models.  Meanwhile, recent studies by
\citet{2017arXiv170306869F,2017arXiv170306223G} focused on inference
on spin magnitudes.

In summary, the angular distribution of spins in \acp{BBH} formed
through isolated binary evolution is uncertain; nevertheless, it is
more probable that spins are preferentially aligned after evolution
through this channel than not, while an isotropic distribution of
spins is the natural outcome of dynamical formation processes.
Therefore, if the current observational trend for low $\chieff$
continues with future gravitational-wave observations, it will be
possible to either confirm that \ac{BH} spins are sometimes large in
magnitude and isotropic in direction, yielding a strong indication of
a dynamical formation origin; or that \ac{BH} spins are overwhelmingly
small in magnitude, yielding a notable contradiction with the claimed
\ac{BH} X-ray binary spin measurements, particularly those for high-mass X-ray
binaries.

@@

The components of this formula are
\begin{itemize}
\item The GW (marginal) likelihood, $p\left(d \mid \chieff\right)$.
  Here we use ``marginal'' because we are (implicitly) integrating
  over all parameters of the signal but $\chieff$.  Note that it is
  the likelihood rather than the posterior that matters for the
  hierarchical analysis; if we are given posterior distributions or
  posterior samples, we need to re-weight to "remove" the prior and
  obtain the likelihood.
\item The population distribution for $\chieff$,
  $p\left( \chieff \mid \lambda \right)$.  This function can be
  parameterised by population-level parameters, $\lambda$.  (In the
  cases discussed above, there are no parameters for the population.)
\item The prior on the population-level parameters, $p(\lambda)$.
\end{itemize}
If we do not care about the individual event $\chieff$ parameters, we
can integrate them out, obtaining
\begin{equation}
  p\left( \lambda \mid \left\{ d^i \right\} \right) \propto \left[ \prod_{i=1}^{N_\mathrm{obs}} \int \dd \chieff^i \, p\left(d^i \mid \chieff^i \right) p\left( \chieff^i \mid \lambda \right) \right] p\left(\lambda\right).
\end{equation}
If we are given posterior samples of $\chieff^{ij}$ ($i$ labels the
event, $j$ labels the particular posterior sample) drawn from an
analysis using a prior $p\left( \chieff \right)$, then we can
approximate the integral by a re-weighted average of the population
distribution over the samples (here $p\left( \chieff^{ij} \right)$ is
the prior used to produce the posterior samples):
\begin{equation}
  p\left( \lambda \mid \left\{ d^i \right\} \right) \propto \left[ \prod_{i=1}^{N_\mathrm{obs}} \frac{1}{N_i} \sum_{j=1}^{N_i} \frac{p\left( \chieff^{ij} \mid \lambda \right)}{p\left( \chieff^{ij} \right)} \right] p\left(\lambda\right).
  \label{eq:hierarchical-posterior}
\end{equation}

@@

It is possible to estimate at an order-of-magnitude level the rate at
which evidence accumulates in favour of or against the isotropic
models as more systems are detected.  Based on Figure
\ref{fig:chieff-distribution-models}, approximate the isotropic
population $\chieff$ distribution as uniform on
$\chieff \in \left[ -0.25, 0.25 \right]$ and the aligned population
$\chieff$ distribution as uniform on
$\chieff \in \left[0, 0.5\right]$.  Then the odds ratio between the
isotropic and aligned models for each event is approximately
\begin{equation}
  \label{eq:approx-odds}
  \frac{p\left( d \mid I \right)}{p\left( d \mid A \right)} \simeq
  \frac{P\left( -0.25 \leq \chieff \leq 0.25 \right)}{P\left( 0 \leq \chieff \leq 0.5 \right) },
\end{equation}
where $P\left( A \leq \chieff \leq B \right)$ is the posterior
probability that $\chieff$ is between $A$ and $B$.  Using our
approximations to the $\chieff$ posteriors described above, this gives
an odds ratio of $5$ in favour of the isotropic models, which is about
a factor of two smaller than the ratio in the more careful calculation
described in Section \ref{sec:O1}.  This is a satisfactory answer at
an order-of-magnitude level.

If the true distribution is isotropic and follows this simple model,
and our measurement uncertainties on $\chieff$ are $\simeq 0.1$, then
each subsequent measurement contributes on average a factor of
$\sim 3$ to the overall odds.  After ten additional events, then, the
odds ratio becomes $5 \times 3^{10} \simeq 3 \times 10^{5}$, or
$4.6 \sigma$, consistent with the results of the more detailed
calculation described above.  If the true distribution of spins
becomes half as wide ($\chieff \in [-0.125, 0.125]$ for isotropic and
$\chieff \in [0, 0.25]$ for aligned spins), with the same
uncertainties, then the existing odds ratio becomes $1.08$, and each
subsequent event drawn from the isotropic distribution contributes on
average a factor of $1.6$.  In this case, after 10 additional events,
the odds ratio becomes $150$, or $2.7\sigma$.  With small spin
magnitudes, our angular resolving power vanishes, as discussed in more
detail in Section \ref{sec:smallspins}.

@@

Here we extend the ``low'' model as:
%
\begin{equation}
p(a) \propto (1 - a)^{\alpha}
\label{eq:lowspinalpha}
\end{equation}
%

When $\alpha = 0$, this recovers the ``flat'' distribution, whilst $\alpha = 1$
recovers the ``low'' distribution. For higher values of $\alpha$, this distribution 
becomes more peaked towards $a = 0$.

%
\begin{figure}
\centering
\includegraphics[width=\textwidth]{../plots/sigma_v_alpha.png}
\caption{\textbf{Effect of small spins on evidence ratio of aligned against isotropic models} The blue line shows the evidence ratio (plotted as the equivalent sigma) between a model where all systems are aligned, versus one where all systems are from an isotropic distribution as a function of the power law $\alpha$ corresponding to Equation~\ref{eq:lowspinalpha}.  The top axis shows the mean spin magnitude $a$
that the value of alpha corresponds to. We see that for mean spin magnitudes $\lesssim 0.2$ we find no evidence for either distribution over the other.}
\label{fig:smallspinsalpha}
\end{figure}
%

In Figure~\ref{fig:smallspinsalpha} we plot the evidence ratio of aligned to isotropic distributions (plotted as the equivalent sigma) with spin magnitudes given by this model with $\alpha$ in the range $0$ -- $6$. The top axis shows the mean spin magnitude
that value of $\alpha$ corresponds to (i.e., for the ``flat'' distribution $\alpha = 0$, the mean spin magnitude is 0.5). We see that if typical BH spins are $\lesssim 0.2$ we have no evidence for one model over the other.

@@

\section{Approximations in the Gravitational Waveform}
The model waveforms used to infer the $\chieff$ of the three events
incorporate approximations to the true behaviour of the merging
systems that are expected to break down for sufficiently high
mis-aligned spins.  The effect of these approximations has been
investigated in detail for the inference on the parameters describing
GW150914 \citep{2016arXiv161107531T}.  For this source, statistical
uncertainties dominate over any waveform systematics.  Detailed
comparisons with numerical relativity computations using no
approximations to the dynamics \citep{2016PhRvD..94f4035A} also
suggest that statistical uncertainties dominate the systematics for
this system.  \citet{2016arXiv161107531T} suggests that systematics
may dominate for signals with this large SNR ($\simeq 23$) when the
source is edge-on or with high spin.  The other two events discussed
in this paper are at much lower SNR, with correspondingly larger
statistical uncertainties, and are probably similarly oriented and
with similarly small spins, so we do not expect systematic
uncertainties to dominate.

Given the preference of our data for a smaller spin population we
assume here that measurements made in the future are not dominated by
systematic errors, but this assumption would need to be revisited for
high-SNR, edge-on, or high-spin sources detected in the future.

>>>>

Estimates of the rate of \ac{BBH} coalescences give a reasonable
chance of 10 additional \ac{BBH} detections in the next two years
\citep{O1-BBH,2016ApJ...833L...1A,2016ApJS..227...14A}.  Assuming \ilya{10} \sout{an}
additional \sout{10} detections with similar observational uncertainties \ilya{[I think it would be useful to specify (in an appendix?) what model we use for the observational uncertainty on $\chieff$.]}
drawn from each of our six zero-parameter models for the spin
distribution in addition to the three existing detections from O1, we
find the odds ratios shown in Figure \ref{fig:O2-predictions}.  We
find that most scenarios with an additional 10 detections allow the
\sout{correct} \ilya{simulated} angular distribution to be \sout{distinguished} \ilya{inferred} with greater than
$5\sigma$ ($2.9 \times 10^{-7}$ odds) credibility; and in the most
pessimistic case the distinction is typically
$\OTwoSigmaIsoAlignedMin\sigma$ ($\OTwoOddsIsoAlignedMin$ odds ratio).
While such future detections should permit a confident distinction
between \emph{angular} distributions, we would remain much less certain
about the \emph{magnitude} distribution \ilya{among the three options considered here} until we have a larger number
of observations.  In Figure \ref{fig:O2-predictions}, the odds ratio
between different magnitude distributions with the same angular
distribution is much closer to unity than the odds ratio between angular
distributions.

@@

Most of our resolving power for the spin angular distribution is a
result of the fact that our ``aligned'' models cannot produce
$\chieff < 0$ (see Figure \ref{fig:chieff-distribution-models}).  If
spins are intrinsically very small, with $\ilya{\chi} \lesssim 0.3$, then it is
no longer possible to resolve the negative \ilya{effective} spin with a small number of
observations.  As noted below, however, spins observed in X-ray
binaries are typically large.  Additionally, models which do not
permit \emph{some} spins with $\chieff \gtrsim 0.1$ are ruled out by
the GW151226 observations \citep{2016PhRvL.116x1103A}.

In order to perform our analysis we need to select models for the
distribution of the spin magnitudes of stellar-mass black holes.
Observational data for such model selection is sparse.
\citet{2015PhR...548....1M} give current estimates of the spin
parameters for stellar-mass black holes, obtained using disk
reflection and/or disk continuum methods.  Most of the systems studied
are low-mass X-ray binaries rather than the high-mass X-ray binaries
that are likely to be the progenitors of double black hole binaries.
In addition, there are substantial systematic errors that can
complicate either type of analysis (see \citealt{2015PhR...548....1M}
for a discussion), and selection effects could yield a biased
distribution. Nonetheless, if we take the reported spin magnitudes as
representative then we find that there is a preference for high spins;
for example, 14 of the 19 systems with reported spins have
dimensionless spin parameters in excess of 0.5.  It is usually argued
that the masses and spin parameters of stellar-mass black holes are
unlikely to be altered significantly by accretion (low-mass donors may
not have enough mass and high-mass donors have a very short phase in
which they transfer mass; a variant of this long-standing argument was
presented by \citet{1999MNRAS.305..654K}), but see
\citet{2003MNRAS.341..385P,2015ApJ...800...17F}.  Thus the current
spin parameters probably are close to their values upon core collapse, \ilya{at least in high-mass X-ray binaries}.
However, the specific processes involved in the production of black
hole binaries from isolated binaries could alter the spin magnitude
distribution of those holes relative to the X-ray binary systems; for
example, close tidal interactions could spin up the core, or stripping
of the envelope could reduce the available angular momentum
\citep{2016MNRAS.462..844K,2017arXiv170200885Z,2017arXiv170203952H}.

@@

The spin directions in isolated binaries, whether evolving via the
classical channel through a common-envelope phase
\citep{TutukovYungelson:1973,TutukovYungelson:1993,Lipunov:1997,2016Natur.534..512B,Stevenson:2017}
or through chemically homogeneous evolution
\citep{MandeldeMink:2016,Marchant:2016} are usually expected to be
preferentially aligned.  Despite observed spin-orbit misalignments in
both massive stellar binaries
\citep{Albrecht:2009,2014ApJ...785...83A} and BH X-ray binaries
\citep{Orosz:2001,Martin:2008b,Martin:2008,MorningstarMiller:2014},
mass accretion and tidal interactions will tend to realign the binary.
On the other hand, a supernova natal kick (if any) can change the
orbital plane and misalign the binary
\citep{2000ApJ...541..319K,2013PhRvD..87j4028G}; the supernova can
also tilt the spin angle, as in the double pulsar J0737-3039
\citep{2011ApJ...742...81F}; and a variety of uncertain processes,
such as wind-driven mass loss and post-collapse fallback, can couple
the spin magnitude and direction distributions, contrary to our
simplified assumptions.

\citet{2017CQGra..34cLT01V} also studied the possibility of
distinguishing aligned and isotropic angular distributions of \ac{BBH}
spins, but concluded that several hundred sources would be required to
adequately separate models which included both parallel and
anti-parallel spins for an ``aligned'' population.  In contrast, and
in agreement with the present study, \citet{Stevenson:2017spin} found
that only $\sim 5$ observations of rapidly spinning black holes would
be necessary to distinguish isotropic and aligned spin distributions,
though tens of detections would be required for more nuanced admixture
models.  Meanwhile, recent studies by
\citet{2017arXiv170306869F} and \citet{2017arXiv170306223G} focused on inference
on spin magnitudes.

In summary, the angular distribution of spins in \acp{BBH} formed
through isolated binary evolution is uncertain; nevertheless, it is
more probable that spins are preferentially aligned after evolution
through this channel than not, while an isotropic distribution of
spins is the natural outcome of dynamical formation processes.
Therefore, if the current observational trend for low $\chieff$
continues with future gravitational-wave observations, it will be
possible to either confirm that \ac{BH} spins are isotropic in direction \ilya{and} sometimes large in
magnitude, yielding a strong indication of
a dynamical formation origin; or that \ac{BH} spins are overwhelmingly
small in magnitude, yielding a notable contradiction with the claimed
\ac{BH} X-ray binary spin measurements, particularly those for high-mass X-ray
binaries.

@@

The components of this formula are
\begin{itemize}
\item The GW (marginal) likelihood, $p\left(d \mid \chieff\right)$.
  Here we use ``marginal'' because we are (implicitly) integrating
  over all parameters of the signal but $\chieff$.  Note that it is
  the likelihood rather than the posterior that matters for the
  hierarchical analysis; if we are given posterior distributions or
  posterior samples, we need to re-weight to ``remove'' the prior and
  obtain the likelihood.
\item The population distribution for $\chieff$,
  $p\left( \chieff \mid \lambda \right)$.  This function can be
  parameterised by population-level parameters, $\lambda$.  (In the
  cases discussed above, there are no parameters for the population.)
\item The prior on the population-level parameters, $p(\lambda)$.
\end{itemize}
If we do not care about the individual event $\chieff$ parameters, we
can integrate them out, obtaining
\begin{equation}
  p\left( \lambda \mid \left\{ d^i \right\} \right) \propto \left[ \prod_{i=1}^{N_\mathrm{obs}} \int \dd \chieff^i \, p\left(d^i \mid \chieff^i \right) p\left( \chieff^i \mid \lambda \right) \right] p\left(\lambda\right).
\end{equation}
If we are given posterior samples of $\chieff^{ij}$ ($i$ labels the
event, $j$ labels the particular posterior sample) drawn from an
analysis using a prior $p\left( \chieff \right)$, then we can
approximate the integral by a re-weighted average of the population
distribution over the samples (here $p\left( \chieff^{ij} \right)$ is
the prior used to produce the posterior samples):
\begin{equation}
  p\left( \lambda \mid \left\{ d^i \right\} \right) \propto \left[ \prod_{i=1}^{N_\mathrm{obs}} \frac{1}{N_i} \sum_{j=1}^{N_i} \frac{p\left( \chieff^{ij} \mid \lambda \right)}{p\left( \chieff^{ij} \right)} \right] p\left(\lambda\right).
  \label{eq:hierarchical-posterior}
\end{equation}

@@

It is possible to estimate at an order-of-magnitude level the rate at
which evidence accumulates in favour of or against the isotropic
models as more systems are detected.  Based on Figure
\ref{fig:chieff-distribution-models}, approximate the isotropic
population $\chieff$ distribution as uniform on
$\chieff \in \left[ -0.25, 0.25 \right]$ and the aligned population
$\chieff$ distribution as uniform on
$\chieff \in \left[0, 0.5\right]$.  Then the odds ratio between the
isotropic and aligned models for each event is approximately
\begin{equation}
  \label{eq:approx-odds}
  \frac{p\left( d \mid I \right)}{p\left( d \mid A \right)} \simeq
  \frac{P\left( -0.25 \leq \chieff \leq 0.25 \right)}{P\left( 0 \leq \chieff \leq 0.5 \right) },
\end{equation}
where $P\left( A \leq \chieff \leq B \right)$ is the posterior
probability \ilya{[Should really be likelihood, not posterior, right?  You are approximating the first term in the product in (B1)...]} that $\chieff$ is between $A$ and $B$.  Using our
approximations to the $\chieff$ posteriors described above, this gives
an odds ratio of $5$ in favour of the isotropic models, which is about
a factor of two smaller than the ratio in the more careful calculation
described in Section \ref{sec:O1}.  This is a satisfactory answer at
an order-of-magnitude level.

If the true distribution is isotropic and follows this simple model,
and our measurement uncertainties on $\chieff$ are $\simeq 0.1$, then
each subsequent measurement contributes on average a factor of
$\sim 3$ to the overall odds. \ilya{[This ranges from $\sim$1 to $\sim$50 (2.5 $\sigma$).  Not clear what an average of 3 means here (geometric mean, I hope?).  I am still not a huge fan of appendix B; it raises more questions than it answers, as far as I am concerned.]}  After ten additional events, then, the
odds ratio becomes $5 \times 3^{10} \simeq 3 \times 10^{5}$, or
$4.6 \sigma$, consistent with the results of the more detailed
calculation described above.  If the true distribution of spins
becomes half as wide ($\chieff \in [-0.125, 0.125]$ for isotropic and
$\chieff \in [0, 0.25]$ for aligned spins), with the same
uncertainties, then the existing odds ratio becomes $1.08$, and each
subsequent event drawn from the isotropic distribution contributes on
average a factor of $1.6$.  In this case, after 10 additional events,
the odds ratio becomes $150$, or $2.7\sigma$.  With small spin
magnitudes, our angular resolving power vanishes, as discussed in more
detail in Section \ref{sec:smallspins}.

@@

Here we extend the ``low'' model as:
%
\begin{equation}
p(\chi) \propto (1 - \chi)^{\alpha}
\label{eq:lowspinalpha}
\end{equation}
%

When $\alpha = 0$, this recovers the ``flat'' distribution, whilst $\alpha = 1$
recovers the ``low'' distribution. For higher values of $\alpha$, this distribution 
becomes more peaked towards $\ilya{\chi} = 0$.

%
\begin{figure}
\centering
\includegraphics[width=\textwidth]{../plots/sigma_v_alpha.png}
\caption{\textbf{Effect of small spins on evidence ratio of aligned against isotropic models.} The blue line shows the evidence ratio (plotted as the equivalent sigma) between a model where all systems are aligned, versus one where all systems are from an isotropic distribution as a function of the power law $\alpha$ corresponding to Equation~\ref{eq:lowspinalpha}.  The top axis shows the mean spin magnitude $\ilya{\chi}$
 \sout{that the value of} \ilya{which this $\alpha$} corresponds to. We see that for mean spin magnitudes $\lesssim 0.2$ we find no evidence for either distribution over the other.  \ilya{[Change $\bar{a}$ to $\bar{\chi}$ on upper abscissa label.]}}
\label{fig:smallspinsalpha}
\end{figure}
%

In Figure~\ref{fig:smallspinsalpha} we plot the evidence ratio of aligned to isotropic distributions (plotted as the equivalent sigma) with spin magnitudes given by this model with $\alpha$ in the range $0$ -- $6$. The top axis shows the mean spin magnitude
that value of $\alpha$ corresponds to (\ilya{e.g.}, for the ``flat'' distribution $\alpha = 0$, the mean spin magnitude is 0.5). We see that if typical BH spins are $\lesssim 0.2$ we have no evidence for one model over the other.

@@

\section{Approximations in the Gravitational Waveform}
The model waveforms used to infer the $\chieff$ of the three LIGO events
incorporate approximations to the true behaviour of the merging
systems that are expected to break down for sufficiently high
mis-aligned spins.  The effect of these approximations \ilya{on inference}  
on the parameters describing
GW150914 has been
investigated in detail \citep{2016arXiv161107531T} \ilya{[Should be an Abbott et al. ref like the others?]}.  For this source, statistical
uncertainties dominate over any waveform systematics.  Detailed
comparisons with numerical relativity computations using no
approximations to the dynamics \citep{2016PhRvD..94f4035A} also
suggest that statistical uncertainties dominate the systematics for
this system.  \citet{2016arXiv161107531T} suggests that systematics
may dominate for signals with this large SNR ($\simeq 23$) when the
source is edge-on or \ilya{has} high spins.  The other two events discussed
in this paper are at much lower SNR, with correspondingly larger
statistical uncertainties, and are probably similarly oriented and
with similarly small spins, so we do not expect systematic
uncertainties to dominate.

\sout{Given the preference of our data for a smaller spin population} We
assume here that measurements made in the future are not dominated by
systematic errors, but this assumption would need to be revisited for
high-SNR, edge-on, or high-spin sources detected in the future.  \ilya{[I thought we argued that there is no strong preference for small spin magnitudes.  We should be consistent...]}
